\documentclass[10pt,aspectration=169]{beamer}
\usepackage{graphicx}
\usepackage{subcaption} % Add the subcaption package for subfigures
\usepackage{hyperref} % Make sure hyperref is loaded after other packages


\usetheme{Warsaw}
\title[CT-Images]{RECONSTRUCTION D'IMAGES ISSUES DE TOMODENSITOMÉTRIE}
\author[Frédéric]{Frédéric ANDRIANARIVONY}
\institute[ESPA Vontovorona]{Département Éléctronique}
\date{\today}

\setbeamertemplate{navigation symbols}{} %Hiding navigation bar at the bottom
\setbeamertemplate{headline}{} %Hiding navigation bar at the top
\setbeamertemplate{frametitle continuation}{}
\setbeamercovered{transparent}


\AtBeginSection[]
{
  \begin{frame}
    \tableofcontents[currentsection]
  \end{frame}
}

\AtBeginSubsection[]
{
  \begin{frame}
    \tableofcontents[currentsection,subsectionstyle=show/shaded/hide]
  \end{frame}
}


\begin{document}
	
    \begin{frame}
        \titlepage
    \end{frame}

    \begin{frame}{Table des Matières}
        \tableofcontents
    \end{frame}

\input{./frames/1. Intro.tex}
\input{./frames/chap1.tex}
\input{./frames/chap2.tex}
\input{./frames/chap3.tex}
\input{./frames/chap4.tex}

	\bibliographystyle{unsrt}
    \begin{thebibliography}{100}
        \bibitem{17} \emph{Comparison between orthogonal and bi-orthogonal wavelets}
        \bibitem{14}  Engl, Heinz W., and R. Ramlau, \emph{Regularization of inverse problems}. Kluwer Academic Publishers, 2000.
        \bibitem{9} Jen Beatty Colby College, \emph{The Radon Transform and the Mathematics of Medical Imaging}
        \bibitem{10} R. Snieder and J. Trampert. \emph{Linear and nonlinear inverse problems}. Department of Geophysics, Utrecht University, P.O. Box 80.021, 3508 TA Utrecht, The Netherlands. Email: snieder@geo.uu.nl.
        \bibitem{11} I. Bloch. \emph{Reconstruction d’images de tomographie}. LTCI, Télécom Paris, Isabelle.Bloch@telecom-paris.fr.
        \bibitem{12} S. Qin. \emph{Simple algorithm for L1-norm regularisation-based compressed sensing and image restoration}. Third Institute of Physics, Georg-August-Universität Göttingen, Friedrich-Hund-Platz 1, Göttingen, Germany. Email: shun.qin@outlook.com.
        \bibitem{13} M. Piening, F. Altekrüger, J. Hertrich, P. Hagemann, A. Walther and G. Steidl. \emph{Learning from small data sets: Patch-based regularizers in inverse problems for image reconstruction}. (Information manquante pour l’affiliation complète). Note: Les affiliations sont indiquées par les chiffres 1 et 2, mais ne sont pas détaillées dans le texte fourni.
        \bibitem{15} Stephen Boyd , Neal Parikh , Eric Chu Borja Peleato and Jonathan Eckstein \emph{Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers}
        \bibitem{18}CANDITIIS, D.D. and VIDAKOVIC, B. (2004) \emph { Wavelet Bayesian Block Shrinkage via Mixtures of Normal-Inverse Gamma Priors}. Journal of Computational and Graphical Statistics, 13 (2), pp. 383-398
        \bibitem{19} LIU, C.-L. (2010) \emph{A Tutorial of the Wavelet Transform}.
        
        \bibitem{20}MEEN, R.S. and SHARMA, A. (2014) \emph{Comparison and Analysis of Orthogonal and Biorthogonal Wavelets for ECG Compression}. International Journal of Research in Engineering and Technology, 3 (3), pp. 242-247.
        \bibitem{21} WIM SWELDENS \emph{THE LIFTING SCHEME: A CONSTRUCTION OF SECOND GENERATION WAVELETS}

        \bibitem{22} Y. Wang, Z. Liu, and H. Chen, \emph{Accurate Image Quality Assessment in Compressive Sensing: Beyond PSNR and MSE}, IEEE Transactions on Image Processing, vol. 33, pp. 2105--2118, 2024. DOI: 10.1109/TIP.2024.3372109.

      \bibitem{23} A. Gupta and R. Singh, \emph{Efficient Error Metrics for Sparse Signal Recovery in Medical Imaging}, Signal Processing, vol. 212, pp. 109145, 2023. DOI: 10.1016/j.sigpro.2023.109145.

      \bibitem{24} Y. Liu, H. Zhang, and Q. Wang, \emph{High-Fidelity Image Recovery in Compressive Sensing: A PSNR-Driven Optimization Framework}, IEEE Transactions on Multimedia, 2024.

      \bibitem{25} W. Simoes and M. De Sa, \emph{PSNR and SSIM: Evaluation of the Imperceptibility Quality of Images Transmitted over Wireless Networks}, Procedia Computer Science, 2024. DOI: 10.1016/j.procs.2024.11.134.


      \bibitem{26} Z. Wang and A. C. Bovik, \emph{Advances in Structural Similarity Metrics for Image Quality Assessment}, IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 45, no. 8, pp. 10212--10227, 2023. DOI: 10.1109/TPAMI.2023.3267890.

      \bibitem{27} H. Li, Y. Liu, and J. Zhang, \emph{SSIM-Based Optimization for Compressive Sensing Reconstruction in Medical Imaging}, Medical Image Analysis, vol. 92, pp. 102987, 2024. DOI: 10.1016/j.media.2023.102987.
      \bibitem{28} Jonathan Richard Shewchuk \emph{An Introduction to the Conjugate Gradient Method Without the Agonizing Pain}
      \bibitem{29} Jeremy E. Cohen \emph{Computing the proximal operator of the $\ell_1$ induced matrix norm}
    \end{thebibliography}
\end{document}
